Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2022-02-17 energy-planning.tex
proofreading

\begin{figure}[t]
  \centering
  \vspace*{-6.8ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{%Illustrative example of planning-scheduling. 
  An initial plan~(in~\ref{sth:i}) is re-planned online changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}). Follow the collected energy data of a physical aerial robot flying the static coverage.}
  \label{fig:il-abs}
  \vspace*{-3.7ex}
\end{figure}

@@

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers forward thrust, and control surfaces maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa. The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
\begin{ctb}
  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies, and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
\end{ctb}

To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.). Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}. Both the variations trajectories are derived for future time instants employing computations and overall energies and battery models. The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}. The overall wraps the past two in a cohesive model that uses differential and periodic modeling to predict future energy behavior of different plans and schedules. In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed-wing aerial robot flying CPP motivates the overall energy model: the evolution is periodic, an observation we exploit in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.

@@

%Using the same notation from Lem.~\ref{lem:new}, 
%
%\begin{equation}\label{eq:nom-cont}
%  \mathbf{u}(t_{j+1}):=\hat{\mathbf{u}}(t_{j+1})-\hat{\mathbf{u}}(t_j),
%\end{equation}
%for all time instants. 
The nominal control and input matrix in Eq.~(\ref{eq:state-perf}) simply includes the change in energy for all time instants, i.e.,
\begin{equation}\label{eq:mat_B}
  \mathbf{u}(t_{j+1})\hspace*{-.5ex}:=\hspace*{-.5ex}\hat{\mathbf{u}}(t_{j+1})\hspace*{-.5ex}-\hspace*{-.5ex}\hat{\mathbf{u}}(t_j),\,\,\,B=\begin{bmatrix}
      0^{1\times\rho} & 1      & \cdots & 1      \\
      0^{1\times\rho} & 0      & \cdots & 0      \\ 
      \vdots          & \vdots & \ddots & \vdots \\
      0^{1\times\rho} & 0      & \cdots & 0   
  \end{bmatrix},
\end{equation}
shifts the base frequency $\alpha_0$ assuming the energy of the computations does not alter the other frequencies. $B\in\mathbb{R}^{m\times n}$ with $n:=\rho+\sigma$ contains zeros but in the first row where the first $\rho$ columns are zeros and the remaining $\sigma$ are ones. Different combinations of $\mathbf{u}$ with matrix $B$ in Eq.~(\ref{eq:mat_B}) are possible, as we discuss briefly in Section~\ref{sec:conclusion}.
The dynamics in Eqs.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as Kalman filter in Section~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric 
conditions.

@@

Let assume for ease of notation that the coverage time evolves linearly. Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
\end{align}\end{subequations} 
$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$ ($\underline{\Gamma},\overline{\Gamma}$)

@@

Let assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.

@@

The section solves the problem in Section~\ref{sec:pbfor}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise. %respectively
%in Sections~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.

@@

Let assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$. 
Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$. The algorithm assumes that the line parallel to ${}^{v_1}|_{v_{|v|}}$ is always connected as it swipes $\mathcal{Q}^{v}$. Nonetheless, complex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and subsequently covering each cell~\cite{choset2001coverage}.% with the novel motion.

@@

      \vspace*{.8ex}
      \IF{$\mathbf{p}(t)=\mathbf{p}_{\Gamma_i}$}
        \STATE $i\gets i+1$\vspace*{.3ex}
        \IF{$i\notin[n]_{>0}$}\label{alg2:cond}
          \STATE $i\gets 1$\vspace*{.3ex}
          \STATE $\varphi_{|\Gamma|+1}\gets$ line in Definition~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
          parallel to ${}^{v_1}|_{v_{|v|}}$ that inter-\vspace*{.5ex} \hspace*{1em}sects $\mathbf{p}_{|\Gamma|}$\vspace*{.3ex}

@@

          \vspace*{.8ex}
          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Definitions~\ref{def:plan}--\hyperref[def:stage]{2}}\label{alg2:last}

@@

An optimal control problem (OCP) that selects the highest configuration of $c_i$ and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories
\begin{subequations}\label{eq:ocp-output-mpc}\begin{align}
  \max_{\mathbf{q}(t),c_i(t)}&{l_f(\mathbf{q}(t_f),t_f)+\int_{t_0}^{t_f}{l(\mathbf{q}(t),c_i(t),t)\,dt}},\label{eq:ocp-costs}\\
  \text{s.t. }\dot{\mathbf{q}}&=f(\mathbf{q}(t),c_i(t),t),\label{eq:dyn-evol}\\
  c_{i,j}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{C}_{i,j},\,c_{i,\rho+k}(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{S}_{i,k}\,\forall j\hspace*{-.2ex}\in\hspace*{-.2ex}[\rho]_{>0},\,k\hspace*{-.2ex}\in\hspace*{-.2ex}[\sigma]_{>0},\label{eq:state-cont-const-mpc}\\
  \mathbf{q}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathbb{R}^m,\,y(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{Y}(t),\label{eq:batt-const-mpc}\\
  \mathbf{q}(t_0)&=\hat{\mathbf{q}}_0\,\,\,\text{given (last estimated state)},\text{ and}\label{eq:ocp-outp-mpc-state-est}\\
  b(t_0)&=b_0\,\,\,\text{given}\label{eq:ocp-outp-bat},
\end{align}\end{subequations}
where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ is a given initial initial cost function with the quadratic expression
\begin{equation}\label{eq:insta-cost-mpc}
  l(\mathbf{q}(t),c_i(t),t)=\mathbf{q}'(t)Q\mathbf{q}(t)+c_i'(t)Rc_i(t),
\end{equation}
where $Q\in\mathbb{R}^{m\times m},R\in\mathbb{R}^{n\times n}$ are given positive semidefinite matrices.%, resulting in the convexity of the cost $l$~\citep{nocedal2006numerical}. A useful property to guarantee a solution~\citep{beck2014introduction}.
The final cost function $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ is also a quadratic expression but with no control~\cite{rawlings2017model}
\begin{equation}\label{eq:final-cost-mpc}
  l_f(\mathbf{q}(T),T)=\mathbf{q}'(T)Q_f\mathbf{q}(T),
\end{equation}
where $Q_f\in\mathbb{R}^{m\times m}$ is a given positive semidefinite matrix.

Furthermore, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}). The model requires a value of the period $T$, which is simply the time needed to fly the four primitive paths in the Zamboni-like motion, i.e., time elapsed between two positive evaluations of the condition on Line~\ref{alg2:cond}.

Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Definition~\ref{def:stage}. Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints in Eq.~(\ref{eq:output-const}) that evolves the battery model in Eq.~(\ref{eq:batdyn}). Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
(the very first estimate is given). Eq.~(\ref{eq:ocp-outp-bat}) is the initial battery SoC from, e.g., flight controller.

@@

Fig.~\ref{fig:trajs} illustrates the same plan $\Gamma$ under different conditions. Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, a wind direction of zero degrees, and initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection). Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Directions}  %
\label{sec:conclusion}                       %
                                             %
The letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending past literature. It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings. Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates the energy of the computing hardware via the \powprof{} tool. The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC. It evolves the state of the energy model while optimizing battery usage and remedying possible defects. The plan compromise multiple stages, where at each the aerial robot flies a path and runs the computations, allowing further extensibility in terms of constructs and approaches.

Indeed, we are currently extending the results to a standard flight controller. The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections), 
and distributed planning-scheduling merits alike further investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots. Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.

Further future directions include the study of different energy models. Among the others, these include, e.g., aperiodic energy models, different linear combinations of the variations of parameters, and stage dependent energy models. In a unconventional setting with, e.g., multiple agent utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.

@@

%A change in the path parameters in Lem.~\ref{lem:new} alters the flight time, and consequently, the energy. The proof quantifies this time: consider the plan $\overline{\Gamma}$ in Fig.~\ref{fig:zambo}. It is composed of four primitive paths and the highest configuration of path parameter $c_{i,1}$. Let assume that the time to travel $\varphi_4(\overline{c}_{i,1})$ is $t_3\in\mathbb{R}_{>0}$, $\varphi_1,\varphi_3$, the two lines, is $2t_1\in\mathbb{R}_{>0}$, and $\varphi_2$ is $t_2\in\mathbb{R}_{>0}$. Further, assume that $v$ is covered merely by the set of primitive paths in Fig.~\ref{fig:zambo}. The coverage time is $t_{\overline{\Gamma}}=7(2t_1+t_2+t_3)+t_1$.

>>>>

\begin{figure}[t]
  \centering
  \vspace*{-6.8ex}
  \begin{tikzpicture}
    \node[inner sep=0pt] () at (0,0)
        {\scriptsize \input{\figpath/new/il_abs.tikz}};
    \node[inner sep=0pt] () at (-2,-5.67)
        {\scriptsize \input{\figpath/il_abs_energy1.tikz}};
    \node[inner sep=0pt] () at (2.1,-5.67)
        {\scriptsize \input{\figpath/il_abs_spectrum1.tikz}};
  \end{tikzpicture}
  \caption{%Illustrative example of planning-scheduling. 
  An initial plan~(in~\ref{sth:i}) is re-planned online, changing the resolution, detection rate, or other computational aspects~(in~\ref{sth:ii}) and changing the number of fly-byes or other motion aspects~(in~\ref{sth:iii}). Follow the collected energy data of a physical aerial robot flying the static coverage.}
  \label{fig:il-abs}
  \vspace*{-3.7ex}
\end{figure}

@@

Our focus is on fixed wings, i.e., airborne robots where wings provide lift, propellers forward thrust, and control surfaces maneuvering. Here, motion and computations energies are within an order of magnitude from each other~\cite{seewald2020mechanical}. Indeed there are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations and vice-versa. The occurrence frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.) and lighter-than-air aerial robots (e.g., blimps). It is a common theme with wider planning-scheduling literature, focusing on energy-efficient ground-based robots such as Pioneer~3DX~\cite{ho2018towards,ho2019learning,ho2019qos,mei2005case}, ARC~Q14~\cite{ondruska2015scheduled,lahijanian2018resource}, and Pack-Bot~UGV~\cite{sadrpour2013mission}.
\begin{ctb}
  We extend the literature on planning-schedu- ling to CPP with aerial robots, model the overall and computations energies and battery evolution, and derive a variable coverage motion for constrained systems, e.g., fixed wings.
\end{ctb}

To guarantee energy awareness, our approach uses optimal control where both the paths and schedules variations are trajectories, varying between given bounds (i.e., physical constraints of the robot and computing hardware, the desired quality of the coverage, etc.). Numerous past planning-scheduling studies also employ optimization techniques~\cite{brateman2006energy,zhang2007low,ondruska2015scheduled,lahijanian2018resource}, whereas some others greedy~\cite{mei2005case,sudhakar2020balancing,sadrpour2013mission} and reinforcement learning-based approaches~\cite{ho2019qos,ho2018towards,ho2019learning}. Both the variations trajectories are derived for future time instants employing computations and overall energies and battery models. The energy model for the computations uses regressional analysis from our earlier study on heterogeneous computing hardware energy modeling~\cite{seewald2019coarse,seewald2019component}, whereas the battery an equivalent circuit model (ECM) from the literature~\cite{he2011evaluation,hinz2019comparison,mousavi2014various}. The overall wraps the past two in a cohesive model that uses dynamics %differential %and periodic 
modeling to predict future energy behavior of different plans and schedules. In Fig.~\ref{fig:il-abs}, collected energy data (bottom left) and spectrum analysis (right) of a fixed wing %aerial robot 
flying CPP motivates the overall energy model: the evolution is periodic, an observation exploited in Section~\ref{sec:energy-model}.% for the computations and motion energies and battery models.

@@

%Using the same notation from Lem.~\ref{lem:new}, 
%
%\begin{equation}\label{eq:nom-cont}
%  \mathbf{u}(t_{j+1}):=\hat{\mathbf{u}}(t_{j+1})-\hat{\mathbf{u}}(t_j),
%\end{equation}
%for all time instants. 
The nominal control and input matrix in Eq.~(\ref{eq:state-perf}) simply includes the change in energy for all time instants, i.e.,
\begin{equation}\label{eq:mat_B}
  \mathbf{u}(t_{j+1})\hspace*{-.5ex}:=\hspace*{-.5ex}\hat{\mathbf{u}}(t_{j+1})\hspace*{-.5ex}-\hspace*{-.5ex}\hat{\mathbf{u}}(t_j),\,\,\,B=\begin{bmatrix}
      0^{1\times\rho} & 1      & \cdots & 1      \\
      0^{1\times\rho} & 0      & \cdots & 0      \\ 
      \vdots          & \vdots & \ddots & \vdots \\
      0^{1\times\rho} & 0      & \cdots & 0   
  \end{bmatrix},
\end{equation}
shifts the base frequency $\alpha_0$ assuming the energy of the computations does not alter the other frequencies. $B\in\mathbb{R}^{m\times n}$ with $n:=\rho+\sigma$ contains zeros but in the first row where the first $\rho$ columns are zeros and the remaining $\sigma$ are ones. Different combinations of $\mathbf{u}$ with matrix $B$ in Eq.~(\ref{eq:mat_B}) are possible, as we discuss briefly in Section~\ref{sec:conclusion}.
The dynamics in Eqs.~(\ref{eq:state-perf}--\ref{eq:mat_B}) additionally allows us to use state estimation techniques, such as the Kalman filter in Section~\ref{sec:repla-algo}, to refine the states $\mathbf{q}$ and model the energy of the aerial robot flying under diverse %atmospheric 
conditions.

@@

For ease of notation, we assume that the coverage time evolves linearly. Path parameters $c_i^\rho$ can be transformed into a time measure with scaling factors\begin{subequations}\label{eq:scale-traj}\begin{align}
  \nu_{i,j}&=\left((\overline{t}-\underline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})\right)/\rho,\\
  \tau_{i,j}&=\left(\underline{c}_{i,j}(\underline{t}-\overline{t})/(\overline{c}_{i,j}-\underline{c}_{i,j})+\underline{t}\right)/\rho,
\end{align}\end{subequations} 
$\forall j\in[\rho]_{>0}$ where $\overline{t},\underline{t}$ are time measures needed to complete the coverage with configurations $\underline{c}_i^\rho,\overline{c}_i^\rho$ ($\underline{\Gamma},\overline{\Gamma}$).

@@

We assume there is at least one measuring device, i.e., shunt or internal power resistor, multimeter, or amperemeter, quantifying the power drain of a specific component, e.g., CPU, GPU, memory, etc., or of the entire computing hardware.

@@

This section solves the problem in Section~\ref{sec:pbfor}. It provides a plan $\Gamma$ and re-plans-schedules such plan energy-wise. %respectively
%in Sections~\ref{sec:cov-algo}--\hyperref[sec:repla-algo]{B}.

@@

We assume the vertices $v_1,v_2,\dots$ are ordered from the top-left-most vertex in clockwise order, the aerial robot can overfly the edges formed by the vertices, and ${}^{v_x}|_{v_y}$ indicates the edge formed by vertices $v_x,v_y$. 
Algorithm~\ref{alg2} details the procedure to generate the plan $\Gamma$ that covers $\mathcal{Q}^v$ per each discretized time step, i.e., $\mathcal{T}:=\{t_0,t_0+h,\dots,t_f\}$ for a given step $h\in\mathbb{R}_{>0}$. The algorithm assumes that the line parallel to ${}^{v_1}|_{v_{|v|}}$ is always connected as it swipes $\mathcal{Q}^{v}$. Nonetheless, a complex covering is possible by, e.g., dividing $\mathcal{Q}^{v}$ into cells to be easily covered and subsequently covering each cell~\cite{choset2001coverage}.% with the novel motion.

@@

      \vspace*{.8ex}
      \IF{$\mathbf{p}(t)=\mathbf{p}_{\Gamma_i}$}
        \STATE $i\gets i+1$\vspace*{.3ex}
        \IF{$i\notin[n]_{>0}$}\label{alg2:cond}
          \STATE $i\gets 1$\vspace*{.3ex}
          \STATE $\varphi_{|\Gamma|+1}\gets$ line in Definition~\ref{def:paths} %in Eq.~(\ref{eq:v1}) 
          parallel to ${}^{v_1}|_{v_{|v|}}$ that\vspace*{.5ex} \hspace*{1em}intersects $\mathbf{p}_{|\Gamma|}$\vspace*{.3ex}

@@

          \vspace*{.8ex}
          \STATE $\Gamma\gets\Gamma\cup\{\Gamma_{|\Gamma|+1},\dots,\Gamma_{|\Gamma|+4}\}${ in Definitions~\ref{def:stage}--\hyperref[def:plan]{4}}\label{alg2:last}

@@

An optimal control problem (OCP) that selects the highest configuration of $c_i$ and respects the constraints, with $\mathbf{q}(t)$ and $c_i(t)$ the state and parameters trajectories
\begin{subequations}\label{eq:ocp-output-mpc}\begin{align}
  \max_{\mathbf{q}(t),c_i(t)}&{l_f(\mathbf{q}(t_f),t_f)+\int_{t_0}^{t_f}{l(\mathbf{q}(t),c_i(t),t)\,dt}},\label{eq:ocp-costs}\\
  \text{s.t. }\dot{\mathbf{q}}&=f(\mathbf{q}(t),c_i(t),t),\label{eq:dyn-evol}\\
  c_{i,j}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{C}_{i,j},\,c_{i,\rho+k}(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{S}_{i,k}\,\forall j\hspace*{-.2ex}\in\hspace*{-.2ex}[\rho]_{>0},\,k\hspace*{-.2ex}\in\hspace*{-.2ex}[\sigma]_{>0},\label{eq:state-cont-const-mpc}\\
  \mathbf{q}(t)&\hspace*{-.2ex}\in\hspace*{-.2ex}\mathbb{R}^m,\,y(t)\hspace*{-.2ex}\in\hspace*{-.2ex}\mathcal{Y}(t),\label{eq:batt-const-mpc}\\
  \mathbf{q}(t_0)&=\hat{\mathbf{q}}_0\,\,\,\text{given (last estimated state)},\text{ and}\label{eq:ocp-outp-mpc-state-est}\\
  b(t_0)&=b_0\,\,\,\text{given}\label{eq:ocp-outp-bat},
\end{align}\end{subequations}
where $l:\mathbb{R}^m\times\mathcal{C}_i\times\mathcal{S}_i\times\mathbb{R}_{\geq 0}\rightarrow\mathbb{R}$ is a given initial cost function with the quadratic expression
\begin{equation}\label{eq:insta-cost-mpc}
  l(\mathbf{q}(t),c_i(t),t)=\mathbf{q}'(t)Q\mathbf{q}(t)+c_i'(t)Rc_i(t),
\end{equation}
where $Q\in\mathbb{R}^{m\times m},R\in\mathbb{R}^{n\times n}$ are given positive semidefinite matrices.%, resulting in the convexity of the cost $l$~\citep{nocedal2006numerical}. A useful property to guarantee a solution~\citep{beck2014introduction}.
The final cost function $l_f:\mathbb{R}^m\times\mathbb{R}_{> 0}\rightarrow\mathbb{R}$ is also a quadratic expression but with no control~\cite{rawlings2017model}
\begin{equation}\label{eq:final-cost-mpc}
  l_f(\mathbf{q}(T),T)=\mathbf{q}'(T)Q_f\mathbf{q}(T),
\end{equation}
where $Q_f\in\mathbb{R}^{m\times m}$ is a given positive semidefinite matrix.

Furthermore, Eq.~(\ref{eq:dyn-evol}) is the differential periodic energy model in Eq.~(\ref{eq:state-perf}). The model requires a value of the period $T$, which is simply the time needed to fly the four primitive paths in the Zamboni-like motion, i.e., the time elapsed between two positive evaluations of the condition on Line~\ref{alg2:cond}.

Eq.~(\ref{eq:state-cont-const-mpc}) are the parameters constraints sets in Definition~\ref{def:stage}. Eq.~(\ref{eq:batt-const-mpc}) are the state and output constraints in Eq.~(\ref{eq:output-const}) that evolve the battery model in Eq.~(\ref{eq:batdyn}). Eq.~(\ref{eq:ocp-outp-mpc-state-est}) is the state guess estimated via state estimation % (e.g., linear Kalman filter)
(the very first estimate is given). Eq.~(\ref{eq:ocp-outp-bat}) is the initial battery SoC from, e.g., flight controller.

@@

Fig.~\ref{fig:trajs} illustrates the same plan $\Gamma$ under different conditions. Flights \hyperref[fig:trajs-I-static]{I}--\hyperref[fig:trajs-dyn-i]{i} have a constant wind speed of five meters per second, a wind direction of zero degrees, and initial parameters $c_{i,1},c_{i,2}$ values of zero and ten (i.e., full $r_2$ and detection). Flights \hyperref[fig:trajs-II-static]{II}--\hyperref[fig:trajs-dyn-ii]{ii} (see added gray background for clarity) are the same but a wind direction of 90 degrees and the initial parameters values of -1000 and two (i.e., minimum $r_2$ and detection).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Directions}  %
\label{sec:conclusion}                       %
                                             %
This letter provides a planning-scheduling approach for autonomous aerial robots powered by a limited power source, extending past literature. It proposes a novel coverage motion for variable CPP robust to aerial robots constraints such as the turning radius of fixed wings. Energy modeling in the letter exploits collected empirical data of the fixed-wing aerial robot flying static CPP and further incorporates the energy of the computing hardware via the \powprof{} tool. The approach compromises two algorithms: one derives a static coverage plan, whereas the other re-plans-schedules the plan on a finite horizon via MPC. It evolves the state of the energy model while optimizing battery usage and remedying possible defects. The plan compromise multiple stages, where at each the aerial robot flies a path and runs the computations, allowing further extensibility in terms of constructs and approaches.

Indeed, we are currently extending the results to a standard flight controller. The guidance on the coverage, coverage with variable altitude, %(for, e.g., infrastructure inspections), 
and distributed planning-scheduling merit alike additional investigation, as well as the study of the implications of planning-scheduling on other energy-critical mobile robots. Here, our preliminary study led to possible savings~\cite{seewald2020beyond}, in line with relevant literature~\cite{ondruska2015scheduled,lahijanian2018resource}.

Further future directions include the study of different energy models. Among the others, these include, e.g., aperiodic energy models, different linear combinations of the variations of parameters, and stage-dependent energy models. In an unconventional setting with, e.g., multiple agents utilized for overall coverage, an agent-dependent model might be employed to achieve energy awareness.

@@

%A change in the path parameters in Lem.~\ref{lem:new} alters the flight time, and consequently, the energy. The proof quantifies this time: consider the plan $\overline{\Gamma}$ in Fig.~\ref{fig:zambo}. It is composed of four primitive paths and the highest configuration of path parameter $c_{i,1}$. We assume that the time to travel $\varphi_4(\overline{c}_{i,1})$ is $t_3\in\mathbb{R}_{>0}$, $\varphi_1,\varphi_3$, the two lines, is $2t_1\in\mathbb{R}_{>0}$, and $\varphi_2$ is $t_2\in\mathbb{R}_{>0}$. Further, assume that $v$ is covered merely by the set of primitive paths in Fig.~\ref{fig:zambo}. The coverage time is $t_{\overline{\Gamma}}=7(2t_1+t_2+t_3)+t_1$.
